Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
BCP: should be the case -> it should be the case
State that hspec generates a report

The \texttt{describe} function combines a list of specs into a larger spec.
% It can be used to organize a spec as a tree.
% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested.  Behavior with evidence that does not
hold is reported to the developer.

@@

\noindent In fact, should be the case that fib returns 0 for all
negative numbers.

>>>>

The \texttt{describe} function combines a list of specs into a larger spec.
% It can be used to organize a spec as a tree.
% Internally, a \texttt{Writer} is used to build up specs in a monadic way.
A spec can be run with the \texttt{hspec} function.  When a spec is
run, all evidence is tested, and a report is generated.
Behavior with evidence that does not hold is marked in the generated
report as {\tt FAILED}.

@@

\noindent In fact, it should be the case that fib returns 0 for all
negative numbers.
